### 2013-12-28 thesis/src/chapters/chapter-5-design.tex
Thesis: Restated HLD overview

As diagram \ref{design:hld-overview} illustrates, we can distinguish two main components of proposed solution: auto-scaling module and inter-cloud broker. Together, they can be seen as an hierarchical autonomic system, where each layer corresponds to a different scalability perspective:
\begin{itemize}
	\item application platform layer: application platform tuning
	\item container layer: vertical scaling
	\item stack layer: horizontal scaling
	\item inter-cloud layer: scaling out across different cloud providers
\end{itemize}

@@

\textbf{data format} & & \\ \specialrule{.1em}{.05em}{.05em}
binary &
-- space-effective

-- unreadable for human
& \\ \hline
character-based &
-- human readable
&
-- ineffective in terms of space
\\ \hline

@@

Among the currently available monitoring systems remarkable are Cloud Watch \cite{CloudWatch}, OpenNebula (Information Manager / Virtual Machine Manager) \cite{OpenNebula} there are also open approaches such as Ganglia Monitoring System \cite{MaChCu04}.

@@

>>>>

Diagram \ref{design:hld-overview} illustrates exemplary Cloud-SAP deployment, among depicted components we can distinguish two main parts of proposed solution: auto-scaling subsystem and inter-cloud broker. Auto-scaling subsystem is responsible for scaling users' application, taking into account different scalability perspectives, handled by a different layers:
\begin{itemize}
	\item application platform layer: application platform tuning
	\item container layer: vertical scaling
	\item stack layer: horizontal scaling
	\item inter-cloud layer: scaling out across different cloud providers
\end{itemize}
The last mentioned layer - inter-cloud - cooperates with different cloud providers, hence, it requires additional work that has to be done. In fact, these extra tasks are delegated to a inter-cloud broker, responsible for a dialog in a cloud federation.

@@

\textbf{data format} & & \\ \specialrule{.1em}{.05em}{.05em}
binary &
-- space-effective
& 
-- unreadable for human
\\ \hline
character-based &
-- human readable
&
-- ineffective in terms of space
\\ \hline

@@

@@

\subsection{Application platform layer}

\subsection{Container layer}
Among the currently available monitoring systems remarkable are Cloud Watch \cite{CloudWatch}, OpenNebula (Information Manager / Virtual Machine Manager) \cite{OpenNebula} there are also open approaches such as Ganglia Monitoring System \cite{MaChCu04}.

\subsection{Stack layer}

\subsection{Cloud layer}
